Excel fun

### 2022-07-13 Excel fun.Rmd
Added code for final(?) version.
Excel experiments.

```{r libraries, include=FALSE}
library(readxl)
library(tidyverse)
```

@@

>>>>

```{r libraries, include=FALSE}
library(readxl)
library(tidyverse)
library(janitor)
```

@@

## Final version?
```{r}
excel <- read_excel("Data/OPXfinans2.xlsx")
excel <- clean_names(excel)

```

## Final final?
```{r}
excel <- read_excel("Data/OPXfinans_final.xlsx")
excel <- clean_names(excel)
excel_united <- excel |> 
  unite(entry, c(category, sub_category, name), sep = " ")
excel_united_wide <- excel_united |> 
  pivot_wider(names_from = entry, values_from = value)
excel_wide <- excel |> 
  pivot_wider(names_from = name, values_from = value) |> 
  arrange(desc(year))
excel_wide <- clean_names(excel_wide)

excel_united_wide <- clean_names(excel_united_wide)

excel_united_wide
united <- excel |> 
  unite(entry, c(category, name), sep = "_")
united <- clean_names(united)
united <- united |> 
  select(-sub_category)
united_wide <- united |> 
  pivot_wider(names_from = entry, values_from = value) |> 
  clean_names()
united_wide
united_wide |> 
  mutate(
    KPI = expenses_fundraising / revenue_private_contributions * 100
  ) |> 
  select(year, firm, KPI)

united_wide |> 
  mutate(
    KPI = (revenue_private_contributions - expenses_fundraising) / revenue_private_contributions * 100
  ) |> 
  select(year, firm, KPI)
```
